Towards Cloud Bursting for Extreme Scale Supercomputers

### 2014-06-30 paper/src/1_introduction.tex
added new command to paper.tex, and update on intro

Our contributions can be summrized as following:
\begin{itemize}
	\item An architecture of I/O burst buffer for increasing data transfer throughput between two systems.
	\item A throughput-based I/O burst buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two systems, a cost-based I/O burst buffer model uses to reduce the total cost and a queue model used.
	%\item 
	\item Evaluating I/O burst buffer architecture and two models by using data obtained from several benchmarks from TSUBAME supercomputer and AMAZON EC2 public cloud.
\end{itemize}
%2
The remainder of this paper is organized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2 
will be shown in section 5, and finally, conclusion and related work will be seen in section 6.

>>>>

Our contributions can be summrized as following:
\begin{itemize}
	\item A cloud-based burst buffer for increasing data transfer throughput between two systems;
	\item A throughput-based I/O burst buffer model, which estimate I/O throughput of systems with I/O burst buffers, and a cost-based I/O burst buffer model, which estimate overall cost give a system configuration;
        \item Evaluating I/O burst buffer architecture and two models by using data obtained from several benchmarks from TSUBAME supercomputer and AMAZON EC2 public cloud.
\end{itemize}
%2
The remainder of this paper is organized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2 
will be shown in section 5, and finally, conclusion and related work will be seen in section 6.
